### 2017-07-19 architecture.tex
Minor changes

Bob, an analyst, authenticates to \NAME and requests access to a private safe collection.
The request is added to the stewarship dashboard and is visiable to all stewards
of that collection. Alice, a steward for the requested
safe collection views and then approves Bob's request for a period of $n$ days.
The approval process adds the appropriate policies to the
safe collection granting access to Bob. Bob now can submit analysis tasks, via
\NAMENS's REST API, that specify data items from the safe collection as inputs.
The REST API marks the analysis task as export controlled since it draws results
from an export controlled safe collection.
The submitted task is posted to an internal queue from which a
worker node in the \NAME private subnet picks up Bob's task. The worker node assumes Bob's identity and with
his credentials requests data from the safe collection. Since Bob now has read privileges for the
safe collection, the data is fetched to the worker node, on which the analysis task is executed.
Upon completion, the worker node puts the generated results in the export-controlled
output directory of the safe collection as the task used export controlled data.
Bob's analysis is now complete, but he is unable to view the
results as they require steward approval. This flow is show in \figurename~\ref{fig:flow1}

@@

\begin{figure*}[ht]
  \center
  \includegraphics[width=\textwidth, height=8cm]{figures/meta-policy.png}
  \caption{Meta-policy specification and configuration}
  \vspace{-1.5em}
  \label{fig:schema}
\end{figure*}

>>>>

Bob, an analyst, authenticates to \NAME and requests access to a private safe collection.
The request is added to the stewarship dashboard and is visible to all stewards
of that collection. Alice, a steward for the requested
safe collection views and then approves Bob's request for a period of $n$ days.
The approval process adds the appropriate policies to the
safe collection granting access to Bob. Bob now can submit analysis tasks through the various
interfaces offered by \NAME, that specify data items from the safe collection as inputs.
The REST API marks the analysis task as export controlled since it draws results
from an export controlled safe collection.
The submitted task is posted to an internal queue from which a
worker node in the \NAME private subnet picks up Bob's task. The worker node assumes Bob's identity and with
his credentials requests data from the safe collection. Since Bob now has read privileges for the
safe collection, the data is fetched to the worker node, on which the analysis task is executed.
Upon completion, the worker node puts the generated results in the export-controlled
output directory of the safe collection as the task used export controlled data.
Bob's analysis is now complete, but he is unable to view the
results as they require steward approval. This flow is show in \figurename~\ref{fig:flow1}

@@

\begin{figure*}%[ht]
  \center
  \includegraphics[width=\textwidth, height=8cm]{figures/meta-policy.png}
  \caption{Meta-policy specification and configuration}
  \vspace{-1.5em}
  \label{fig:schema}
\end{figure*}
